---
title: "Econ1 Students' Feedbacks Analysis"
author: "Yongxin (Yong) GUO, s2093198"
output: github_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include = FALSE}
library(tidyverse)
library(readxl)
library(tidymodels)
library(dsbox)
```

```{r load-data, message = FALSE}
econ1 <- read_excel("econ1feed.xlsx")
```

```{r relevel-1}
econ1_1 <- econ1 %>% 
  mutate(
    `compare-school` = case_when(
      `compare-school` == "Better" ~ "Better",
      `compare-school` %in% c("Worse", "About the same", NA) ~ "Not better"
  ))
```

```{r bootstrapped-data-frame-1}
set.seed(1000)
boot_df_1 <- econ1_1 %>% 
  specify(response = `compare-school`, success = "Better") %>% 
  generate(reps = 15000, type = "bootstrap") %>% 
  calculate(stat = "prop")
```

```{r result-1}
boot_df_1 %>%
  summarize(lower = quantile(stat, 0.125),
            upper = quantile(stat, 0.875))
```

We are 75% confident to say that amongth the current Economics 1 students, the proportion of students, who feel their experience at School of Economics is better than other schools, is roughly between 11% and 21%.


```{r relevel-2}
econ1_2 <- econ1 %>% 
  mutate(
    `compare-school` = case_when(
      `compare-school` == "Worse" ~ "Worse",
      `compare-school` %in% c("Better", "About the same", NA) ~ "Not worse"
  ))
```

```{r bootstrapped-data-frame-2}
set.seed(1000)
boot_df_2 <- econ1_2 %>% 
  specify(response = `compare-school`, success = "Not worse") %>% 
  generate(reps = 15000, type = "bootstrap") %>% 
  calculate(stat = "prop")
```

```{r result-2}
boot_df_2 %>%
  summarize(lower = quantile(stat, 0.125),
            upper = quantile(stat, 0.875))
```

We are 75% confident to say that amongth the current Economics 1 students, the proportion of students, who feel their experience at School of Economics is not worse than other schools, is roughly between 72% and 84%.


```{r relevel-3}
econ1_3 <- econ1 %>% 
  mutate(
    `compare-course` = case_when(
      `compare-course` == "Better" ~ "Better",
      `compare-course` %in% c("Worse", "About the same", NA) ~ "Not better"
  ))
```

```{r bootstrapped-data-frame-3}
set.seed(1000)
boot_df_3 <- econ1_3 %>% 
  specify(response = `compare-course`, success = "Better") %>% 
  generate(reps = 15000, type = "bootstrap") %>% 
  calculate(stat = "prop")
```

```{r result-3}
boot_df_3 %>%
  summarize(lower = quantile(stat, 0.125),
            upper = quantile(stat, 0.875))
```

We are 75% confident to say that amongth the current Economics 1 students, the proportion of students, who feel their experience in Economics 1 is better than other courses, is roughly between 5% and 16%.


```{r relevel-4}
econ1_4 <- econ1 %>% 
  mutate(
    `compare-course` = case_when(
      `compare-course` == "Worse" ~ "Worse",
      `compare-course` %in% c("Better", "About the same", NA) ~ "Not worse"
  ))
```

```{r bootstrapped-data-frame-4}
set.seed(1000)
boot_df_4 <- econ1_4 %>% 
  specify(response = `compare-course`, success = "Not worse") %>% 
  generate(reps = 15000, type = "bootstrap") %>% 
  calculate(stat = "prop")
```

```{r result-4}
boot_df_4 %>%
  summarize(lower = quantile(stat, 0.125),
            upper = quantile(stat, 0.875))
```

We are 75% confident to say that amongth the current Economics 1 students, the proportion of students, who feel their experience in Economics 1 is not worse than other courses, is roughly between 72% and 84%.


```{r relevel-5}
econ1_5 <- econ1 %>% 
  mutate(
    `compare-tut` = case_when(
      `compare-tut` == "Better" ~ "Better",
      `compare-tut` %in% c("Worse", "About the same", NA) ~ "Not better"
  ))
```

```{r bootstrapped-data-frame-5}
set.seed(1000)
boot_df_5 <- econ1_5 %>% 
  specify(response = `compare-tut`, success = "Better") %>% 
  generate(reps = 15000, type = "bootstrap") %>% 
  calculate(stat = "prop")
```

```{r result-5}
boot_df_5 %>%
  summarize(lower = quantile(stat, 0.125),
            upper = quantile(stat, 0.875))
```

We are 75% confident to say that amongth the current Economics 1 students, the proportion of students, who feel their Economics 1 tutorial experience is better than tutorials of other courses, is roughly between 14% and 25%.


```{r relevel-6}
econ1_6 <- econ1 %>% 
  mutate(
    `compare-tut` = case_when(
      `compare-tut` == "Worse" ~ "Worse",
      `compare-tut` %in% c("Better", "About the same", NA) ~ "Not worse"
  ))
```

```{r bootstrapped-data-frame-6}
set.seed(1000)
boot_df_6 <- econ1_6 %>% 
  specify(response = `compare-tut`, success = "Not worse") %>% 
  generate(reps = 15000, type = "bootstrap") %>% 
  calculate(stat = "prop")
```

```{r result-6}
boot_df_6 %>%
  summarize(lower = quantile(stat, 0.125),
            upper = quantile(stat, 0.875))
```

We are 75% confident to say that amongth the current Economics 1 students, the proportion of students, who feel their Economics 1 tutorial experience is not worse than tutorials of other courses, is roughly between 79% and 90%.




